Ornaments as indicators of social changes in northeastern Taiwan before and after the European colonial period

### 2020-07-07 analysis/paper/paper.Rmd
edit the chronology section

Based on the copies of original excavation records, we have made refinements of the original chronology to assign contexts into the pre-European, European, and the Chinese periods with six steps of assigning and evaluations. First, we determined the context with indirect colonial impacts including the Europeans and the Chinese according to the higher frequency of time indicators. Second, we examined the description of color and texture changes in strategrphic data to identify the end of the context. Third, we checked whether there are radiocarbon ages from the context and if there are any conflicts or ambiguities to decide the usefulness of the ages. Fourth, we evaluated if there are any post-depositional issues to exclude problematic data. Fifth, we cross evaluated all fourty squares to make sure a consistent stratigraphic context across them. Sixth, we cross evaluated our chronology by checking previous studies of assigning chronology to make a final decision [@Hsieh2009; @Wang2011]. We also provide Supplementary Online Materials that include the details of stratigraphic data, the high frequency of time indicators, and the decision making during the assigning process.

>>>>

## Method for assigning ornaments

Based on the copies of original excavation records and fieldwork notes, we have made refinements of the original chronology to assign contexts into the pre-European, European, and the Chinese periods with six steps of assigning and evaluations. First, we determined the artificial layer (mostly 10 cm) with indirect colonial impacts according to the finding of high frequency of time indicators representing the European and the Chinese period. Second, we identified the complete context (normally consists of 2-3 layers) where the layer belongs to based on the description of soil color, soil texture, and unearthed artifacts using original strategrphic data. Third, we checked if there are radiocarbon ages associated with the context as a cross validation. Since we noted that the radiocarbon ages normally represent long time ranges, the ages are not considered if they cannot provide useful information. Fourth, we examined the original fieldwork notes to identify any post-depositional issues that might affect the deposition of time indicators to ensure an appropriate assignment. Fifth, we cross evaluated all adjacent squares to confirm a consistent, and continuous context between them. Sixth, we compared our chronology with six analytic units classified by previous studies to make a final decision [@Hsieh2009; @Wang2011]. More detailed data information is in Supplementary Online Materials. After assigning the contexts into the pre-European contact, the European presence, and the Chinese presence, we decided the chronology of ornaments by examining in which context they were found. Through those assigning steps with validation rules, we believe our chronology is reasonable and suitable for discussing the indirect colonial impacts led by trade networks.
